\documentclass[10pt,aspectratio=169]{beamer}
\usetheme{metropolis}

\title{swipeWrite}
\date{}
\author{
  Aishvarya \and
  Dyuthi \and
  Durga \and
  Swetha
}

\begin{document}

\maketitle

\begin{frame}{Problem Statement}
  \begin{itemize}
    \item Traditional input methods can be restrictive.
    \item Can hinder creativity and inclusivity for users with physical limitations.
  \end{itemize}
\end{frame}

\begin{frame}{Solution}
  Gesture controlled whiteboard application to create digital drawings through intuitive hand gestures.
  \begin{itemize}
    \item Utilizes computer vision and machine learning.
    \item Enables drawing without a mouse or stylus.
  \end{itemize}
\end{frame}

\begin{frame}{Approach}
  \begin{enumerate}
    \item Hand Tracking 
    \item Gesture recognition using hand coordinates 
    \item Develop a simple whiteboard application.
    \item Modify the whiteboard to take inputs from the real-time video feed to draw.
  \end{enumerate}
\end{frame}

\begin{frame}{Tech Stack}
  \begin{itemize}
    \item Python
    \item OpenCV
    \item Mediapipe
    \item HTML, CSS, JavaScript
    \item Flask
    \item SocketIO
  \end{itemize}
\end{frame}

\begin{frame}{Challenges}
  \begin{itemize}
    \item Lack of documentation in Mediapipe
    \item Integrating with the frontend in real-time 
    \item Writing is shaky.
  \end{itemize}
\end{frame}

\begin{frame}{Future Scope}
  \begin{itemize}
    \item Improve the UI.
    \item Implement OCR for handwriting recognition.
    \item Whiteboard save feature.
    \item Presentations with SwipeWrite 
  \end{itemize}
\end{frame}

\end{document}
